Motional Ground State Cooling Outside the Lamb-Dicke Regime

### 2017-08-09 geometry.tex
Polarizations

  \begin{scope}[transform canvas={rotate={4}}]
    \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.2};
    \path (3.4, 0) node[above,orange!80!black] {Raman F2};
    \path (3, 0) node[below,orange!80!black] {\textbf{R3}};
  \end{scope}

  \draw[orange!50!black, <->, densely dotted, >=stealth, line width=0.8]
  (3:3.4) arc (3:-32:3.4 and 1.65);
  \path (-6:3.3) node[orange!50!black, right] {$42^\circ$};

  \begin{scope}[transform canvas={cm={1,-0.28,0,1,(0, 0)}}]
    \draw[blue, dotted, line width=0.5] (-4.0, 0) -- (4.0, 0);

    \fill[blue!50!black,opacity=0.1] (-2.5, 2.7) -- (2.5, 2.7)
    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
    \draw[blue!50!black, densely dotted,line width=0.6] (-2.5, 2.7) -- (2.5, 2.7)
    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
    \arrowthreeD{red}{(0, -0.4)}{180}{0.4}{1.4};
    \arrowthreeD{orange}{(-0.4, 0)}{90}{0.4}{1.4};
    \arrowthreeD{blue}{(0.4, 0)}{-90}{0.4}{1.4};
    \arrowthreeD{red}{(0, 0.4)}{0}{0.4}{1.4};
    \path (1.6, 0) node[below,blue!80!black] {OP};
    \path (-1.6, 0) node[above,orange!80!black] {Raman F2};
    \path (-1.6, 0) node[below,orange!80!black] {\textbf{R1}};

    \path (0, 1.7) node[left,red!80!black] {Raman F1};
    \path (0, 1.7) node[right,red!80!black] {\textbf{R2}};

    \path (0, -1.7) node[left,red!80!black] {\textbf{R4}};
    \path (0, -1.7) node[right,red!80!black] {Raman F1};

    \draw[white,opacity=0.5,->,>=stealth,line width=1.5] (2.21, 2.39) -- (0.81, 2.39);
    \draw[->,>=stealth,line width=1.5] (2.2, 2.4) -- (0.8, 2.4);
    \path (1.51, 2.39) node[below,white,opacity=0.5] {B field};
    \path (1.5, 2.4) node[below] {B field};
  \end{scope}

>>>>

  \begin{scope}[transform canvas={rotate={4}}]
    \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.4};
    \path (3.33, 0) node[above,orange!80!black] {Raman F2};
    \path (2.9, 0) node[below,orange!80!black] {\textbf{(R3)}};
  \end{scope}
  \draw[->,>=stealth,line width=0.8,color=black!60] (4:4.4) -- ++ (90-30:0.3);
  \draw[->,>=stealth,line width=0.8,color=black!60] (4:4.4) -- ++ (90-30:-0.3);

  \draw[orange!50!black, <->, densely dotted, >=stealth, line width=0.4]
  (3:3.4) arc (3:-32:3.4 and 1.65);
  \path (-6:3.3) node[orange!50!black, right] {$42^\circ$};

  \draw[line width=0.8,color=black!60] (2.2, -0.25-2.2*0.28) arc (-90:60:0.13 and 0.25);
  \draw[->,>=stealth,line width=0.8,color=black!60]
  (-2.24, -0.25+2.24*0.28) arc (-90:40:0.13 and 0.25);

  \begin{scope}[transform canvas={cm={1,-0.28,0,1,(0, 0)}}]
    \draw[->,>=stealth,line width=0.8,color=black!60] (-0.23, 2.2) arc (180:35:0.23 and 0.13);
    \draw[line width=0.8,color=black!60] (-0.23, -2.2) arc (180:35:0.23 and 0.13);

    \draw[blue, dotted, line width=0.5] (-4.0, 0) -- (4.0, 0);

    \fill[blue!50!black,opacity=0.1] (-2.5, 2.7) -- (2.5, 2.7)
    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
    \draw[blue!50!black, densely dotted,line width=0.6] (-2.5, 2.7) -- (2.5, 2.7)
    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
    \arrowthreeD{red}{(0, -0.4)}{180}{0.4}{1.6};
    \arrowthreeD{orange}{(-0.4, 0)}{90}{0.4}{1.6};
    \arrowthreeD{cyan!40!blue}{(0.4, 0)}{-90}{0.4}{1.6};
    \arrowthreeD{red}{(0, 0.4)}{0}{0.4}{1.6};
    \path (1.6, 0) node[below,cyan!20!blue!80!black] {OP};
    \path (-1.25, 0) node[above,orange!80!black] {Raman F2};
    \path (-1.6, 0) node[below,orange!80!black] {\textbf{(R1)}};

    \path (0, 1.5) node[left,red!80!black,align=center] {Raman F1\\\textbf{(R2)}};

    \path (0, -1.7) node[right,red!80!black,align=center] {Raman F1\\\textbf{(R4)}};

    \draw[white,opacity=0.5,->,>=stealth,line width=1.5] (2.21, 2.39) -- (0.81, 2.39);
    \draw[->,>=stealth,line width=1.5] (2.2, 2.4) -- (0.8, 2.4);
    \path (1.51, 2.39) node[below,white,opacity=0.5] {B field};
    \path (1.5, 2.4) node[below] {B field};

    \draw[line width=0.8,color=black!60] (-0.23, 2.2) arc (180:330:0.23 and 0.13);
    \draw[->,>=stealth,line width=0.8,color=black!60] (-0.23, -2.2) arc (180:330:0.23 and 0.13);
  \end{scope}

  \draw[->,>=stealth,line width=0.8,color=black!60]
  (2.2, -0.25-2.2*0.28) arc (-90:-250:0.13 and 0.25);
  \draw[line width=0.8,color=black!60]
  (-2.24, -0.25+2.24*0.28) arc (-90:-240:0.13 and 0.25);
